Pyg4ometry: a Python library for the creation of Monte Carlo radiation transport physical geometries

### 2020-03-02 public/paper/pyg4ometry.tex
paper push

@@

Coplanar faces, in which the faces of two union components or that of
two regions are perfectly coplanar in FLUKA are ubiquitous and present
no difficulties to the operation of the program.  However, in Geant4
these will generally result in tracking errors.  These must be handled
robustly to ensure the resulting geometry is usable.  Coplanar faces
are resolved automatically by slightly decreasing the size of every
body that is used in an intersection, and increasing the size of every
body used in a subtraction.  These rules are inverted for nested
subtractions and work well for guaranteeing well-formed geometry free
from overlaps.

@@

@@

\subsection{Conclusion?}

>>>>

The above algorithm for replacing infinite FLUKA bodies with finite
Geant4 solids works well in most cases, but additional care must be
taken for redundant infinite half spaces.  A redundant infinite half
space is defined as one which has no affect on the topology of the
final Boolean solid.  Whilst this may be true of arbitrary bodies, it
is most problematic for half spaces as after the infinite-body
reduction has been performed, if the half-space is far away from the
region's AABB, then it can result in a malformed Boolean.  This is
demonstrated in Figure~\ref{fig:redundant-halfspace}.  Such
half-spaces are filtered from their respective regions during the
conversion process by calculating the nearest distance from the centre
of the AABB to the half-space face.  If this distance is greater than
the centre-to-corner distance of the AABB, then that half-space is
removed from the region during conversion.

@@

Coplanar faces, in which the faces of two union components or that of
two regions are perfectly coplanar in FLUKA are ubiquitous and present
no difficulties to the operation of the program.  However, in Geant4
these will generally result in tracking errors.  These must be handled
robustly to ensure the resulting geometry is usable.  Coplanar faces
are resolved automatically by slightly decreasing the size of every
body that is used in an intersection, and increasing the size of every
body used in a subtraction.  These rules are inverted for nested
subtractions and work well for guaranteeing well-formed geometry that
is free from overlaps.

@@

A disjoint union in FLUKA is a union of two or more zones that are not
connected.  This is a valid construct in FLUKA but is explicitly
forbidden in Geant4 and must be removed during the conversion
process.  Disjoint unions are detected by checking for overlaps
between all zones within a union.

@@

Description of how we translate lattices into one LV with multiple PVs.
